\chapter{Introduction}
\section{introduction to UI}
\subitem{
	the ‘Ui’ user interface … IS everything DESIGNED TO work on device to that human interact with it. no matter what... like display screen, MOUSE, and windows APPLICATION or WEB sites ... and mobile application. and ui concerned with color and SHAPE...
	ui is in everything that around US.
	}
\section{introduction to UX}
\subitem{
	User experience design (UXD or UED) is the process of enhancing customer satisfaction and loyalty by improving the usability, ease of use, and pleasure provided in the interaction between the customer and the product. so if we talking about the general vision of a design in an application so it will be the UX DESIGN.
	}
\section{ui vs ux}
\subitem{
	Citations: 
	1. “UX is focused on the user’s journey to solve a problem, UI is focused on how a product’s surfaces look and function”. Ken Norton – Partner at Google Ventures
	2. “A UX designer is concerned with the conceptual aspects of the design process, leaving the UI designer to focus on the more tangible elements”. Andy Budd – Co-founder of Clearleft
	3. “There is no difference between UX and UI design because they are two things that aren’t comparable to each other”. Craig Morrison – Head of Product at RecordSetter
	
	4. “UI is generally about visual design and information design around screens. UX is about the complete experience, and it may not be even about the screen” Patrick Neeman – Director of Product Design at Apptio
	
	5. “UI is focused on the product, a series of snapshots in time. UX focuses on the user and their journey through the product” Scott Jenson – Product Strategist at Google
	
	6. “UX is the overall experience a user has with the product, and UI is the things the user will actually interact with and see” Clayton Yan – User Experience Designer at UserTesting
	
	}